Explore immune cell types in Ewing sarcoma

### 2025-03-20 analyses/infercnv-consensus-cell-type/exploratory-notebooks/01_ewings-consensus-cell-types.Rmd
Update analyses/infercnv-consensus-cell-type/exploratory-notebooks/01_ewings-consensus-cell-types.Rmd
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>

These results show macrophage and T cells, which are the two most prevalent categories immune cell categories.
We might want to investigate these cells further, but at least we should probably exclude them as "normal" cells for `inferCNV` since their true status is bit unclear.

>>>>

These results show macrophage and T cells, which are the two most prevalent categories immune cell categories.
We might want to investigate these cells further, but at least we should probably exclude them as "normal" cells for `inferCNV` since their true status is a bit unclear.
